\documentclass[10pt]{extarticle}

% Settings file
\input{page-formatting}

\def\authorName{Felipe Fronchetti}
\def\universityName{Virginia Commonwealth University}
\def\DepartmentName{Department of Computer Science}
\def\authorEmail{fronchettl@vcu.edu}
\def\authorWebsite{https://fron.ch/}

\begin{document}
\createHeader

\section{Summary}
\small Fronchetti is a Ph.D. Student in Computer Science at Virginia Commonwealth University, USA. Currently working on the intersection between Software Engineering (SE) and Human-Robot Interaction (HRI), his work focuses on the development of programming tools for end-users in industrial robotics. Previously, he also researched topics in the open-source development context, including but not limited to the integration of newcomers in open-source projects, the differences between employees and volunteers in open-source communities, and the benefits of social coding platforms. With more than 7 years of experience in research, his work resulted in 17 papers published in top-tier journals and conferences, including ICSE, TSE, EMSE, and FSE (citations: 206, h-index: 9). He also contributed as a committee member for MSR and RoPES and was the web chair of the DREE workshop.

\section{Education}
\newDegree{Ph.D. in Computer Science}{Virginia Commonwealth University (VCU), USA}{Dr. David Shepherd}{``Developing tools to support end-users in robot programming''}{2020 - present}
%
\newDegree{M.Sc. in Computer Science}{University of São Paulo (USP), Brazil}{Dr. Marco Aurélio Gerosa}{``A classification model to identify newcomer-relevant documentation''\\ in open-source software projects}{2018 - 2022}
%
\newDegree{B.Sc. in Computer Science}{Federal University of Technology - Paraná (UTFPR), Brazil}{Dr. Igor Steinmacher and Dr. Igor Wiese}{``An exploratory study on receptivity indicators in open-source software projects''}{2013 - 2017}
%
\newDegreeShort{Technical Degree in Occupational Health and Safety}{National Service for Industrial Training (SENAI), Brazil}{2011 - 2012}

\section{Publications}
%%%%%%%%%%%%%%%%%%
%   JOURNALS     %
%%%%%%%%%%%%%%%%%%
\subsection{Journals (4)}
\newPaper{2022}{\underline{Fronchetti, F.}, Ritschel, N., Holmes, R., Li, L., Soto, M., Jetley, R., Wiese, I. and Shepherd, D., 2022. Language impact on productivity for industrial end users: A case study from Programmable Logic Controllers. In \textbf{Journal of Computer Languages (COLA)}, 69, p.101087.}
%
\newPaper{2020}{Padala, H.S., Mendez, C., \underline{Fronchetti, F.}, Steinmacher, I., Steine-Hanson, Z., Hilderbrand, C., Horvath, A., Hill, C., Simpson, L., Burnett, M. and Gerosa, M., 2020. How gender-biased tools shape newcomer experiences in OSS projects. In IEEE \textbf{Transactions on Software Engineering (TSE)}, 48(1), pp.241-259.}
%
\newPaper{2018}{\underline{Dias, L.F.}, Steinmacher, I. and Pinto, G., 2018. Who drives company-owned OSS projects: internal or external members?. In \textbf{Journal of the Brazilian Computer Society (JBCS)}, 24(1), pp.1-17.}
%
\newPaper{2018}{Pinto, G., Steinmacher, I., \underline{Dias, L.F.} and Gerosa, M., 2018. On the challenges of open-sourcing proprietary software projects. In \textbf{Empirical Software Engineering (EMSE)}, 23, pp.3221-3247.}
\\
%%%%%%%%%%%%%%%%%%
%  CONFERENCES   %
%%%%%%%%%%%%%%%%%%
\subsection{Conferences (13)}
\newPaper{2024}{\underline{Fronchetti, F.}, Ritschel, N., Schorr, L., Barfield, C., Chang, G., Spinola, R., Holmes, R. and Shepherd, D.C., 2024. April. Block-based Programming for Two-Armed Robots: A Comparative Study. In Proceedings of the ACM/IEEE 45th \textbf{International Conference on Software Engineering (ICSE): Research Track}.}
%
\newPaper{2023}{Ruvimova, A., \underline{Fronchetti, F.}, Khan, B., Susin, L., Hurley, Z., Fritz, T., Hancock, M., Shepherd, D.C., 2023, December. Ready Worker One? High-Res VR for the Home Office. In Proceedings of the 29th ACM \textbf{Symposium on Virtual Reality Software and Technology (VRST)}.}
%
\newPaper{2023}{\underline{Fronchetti, F.}, Shepherd, D.C., Wiese, I., Treude, C., Gerosa, M. and Steinmacher, I, 2023. December. Do CONTRIBUTING files provide information about OSS newcomers' onboarding barriers? In Proceedings of the ACM Joint European \textbf{Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE)}.}
%
\newPaper{2022}{Ritschel, N., \underline{Fronchetti, F.}, Holmes, R., Garcia, R. and Shepherd, D.C., 2022, May. Enabling end-users to implement larger block-based programs. In Proceedings of the ACM/IEEE 44th \textbf{International Conference on Software Engineering (ICSE): Companion Proceedings} (pp. 347-349).}
%
\newPaper{2022}{Shepherd, D.C., \underline{Fronchetti, F.}, Liu, Y., Hou, D., DeWaters, J. and Small, M.M., 2022, May. Project-sized scaffolding for software engineering courses. In Proceedings of the First \textbf{International Workshop on Designing and Running Project-Based Courses in Software Engineering Education (DREE)} (pp. 27-31).}
%
\newPaper{2022}{Ritschel, N., \underline{Fronchetti, F.}, Holmes, R., Garcia, R. and Shepherd, D.C., 2022. Can guided decomposition help end-users write larger block-based programs? a mobile robot experiment. Proceedings of the \textbf{ACM on Programming Languages (OOPSLA)}, pp.233-258.}
%
\newPaper{2020}{\underline{Dias, L.F.}, Barbosa, C., Pinto, G., Steinmacher, I., Fonseca, B., Ribeiro, M., Treude, C. and Da Costa, D.A., 2020, August. Refactoring from 9 to 5? What and When Employees and Volunteers Contribute to OSS. In 2020 \textbf{IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC)} (pp. 1-5). IEEE.}
%
\newPaper{2019}{\underline{Fronchetti, F.}, Wiese, I., Pinto, G. and Steinmacher, I., 2019, May. What Attracts Newcomers to Onboard on OSS Projects? TL; DR: Popularity. In 15th IFIP \textbf{International Conference on Open Source Systems (OSS)} (pp. 91-103).}
%
\newPaper{2018}{Pinto, G., \underline{Dias, L.F.} and Steinmacher, I., 2018, May. Who gets a patch accepted first? comparing the contributions of employees and volunteers. In Proceedings of the 11th \textbf{International Workshop on Cooperative and Human Aspects of Software Engineering (CHASE)} (pp. 110-113).}
%
\newPaper{2018}{Pinto, G., Wiese, I. and \underline{Dias, L.F.}, 2018, March. How do scientists develop scientific software? An external replication. In 2018 \textbf{IEEE International Conference on Software Analysis, Evolution and Reengineering (SANER)} (pp. 582-591). IEEE.}
%
\newPaper{2017}{\underline{Dias, L.F.}, Steinmacher, I. and Pinto, G., 2017. Who drives company-owned OSS projects: Employees or volunteers?. In \textbf{V Workshop on Software Visualization, Evolution and Maintenance (VEM)}, co-located with CBSoft (p. 10).}
%
\newPaper{2016}{\underline{Dias, L.F.}, Steinmacher, I., Pinto, G., Da Costa, D.A. and Gerosa, M., 2016, October. How does the shift to GitHub impact project collaboration?. In 2016 \textbf{IEEE International Conference on Software Maintenance and Evolution (ICSME)} (pp. 473-477). IEEE.}
%
\newPaper{2016}{\underline{Dias, L.F.}, Steinmacher, I., Wiese, I., Pinto, G., da Costa, D.A., Gerosa, M. and Mourao–PR–Brasil, C., Uma Análise Preliminar de Projetos de Software Livre que Migraram para o GitHub. In \textbf{IV Workshop on Software Visualization, Evolution and Maintenance (VEM)}, co-located with CBSoft.}

\section{Work}
\newWork{2020 - present}{Graduate Research And Teaching Assistant (Full-time)}{Virginia Commonwealth University (VCU), USA}
\newWork{2018 - 2019}{Graduate Research Assistant (Full-time)}{University of São Paulo (USP), Brazil}
\newWork{2014 - 2016}{Co-Founder and Marketing Director (Part-time)}{HAKEN - Junior Enterprise in Computer Science, Brazil}
\newWork{2014 - 2017}{Undegraduate Research Assistant (Part-time)}{Federal University of Technology - Paraná (UTFPR), Brazil}
\newWork{2012 - 2012}{Occupational Health and Safety Intern (Part-time)}{Beeight Group, Brazil}

\section{Service}
\subsection{Program Committee}
\newService{2023}{Member}{Mining Software Repositories (MSR)}
\newService{2022}{Member}{International Workshop on Recruiting Participants for Empirical Software Engineering (RoPES)}
\newService{2022}{Sub-reviewer}{International Symposium on Open Collaboration (OpenSym)}
\newService{2019}{Sub-reviewer}{Brazilian Symposium on Collaborative Systems (SBSC)}

\subsection{Event Organization}
\newService{2022}{Web Chair}{Workshop on Designing and Running Project-Based Courses in Software Engineering Education (DREE)}
\newService{2021}{Session Chair}{Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE)}
\newService{2021}{Session Chair}{International Conference on Automated Software Engineering (ASE)}
\newService{2020}{Session Chair}{International Conference on Global Software Engineering (ICGSE)}

\section{Talks}
\newTalk{2022}{Speaker}{Is robot programming for everyone? A study about end-users in robotics.\\ College of William \& Mary, Virginia, USA.}
\newTalk{2022}{Speaker}{Talking with robots: Why is it so tricky, and how can we improve it?\\ Full Steam Ahead Middle School Conference, Virginia, USA.}

\section{Teaching}
\newTeaching{2023}{Instructor}{Introduction to Mixed Reality and Industrial Robotics (10 hours).\\ Software Engineering Hands-On Day. Virginia Commonwealth University.}
\newTeaching{2023}{Teaching Assistant}{Fundamentals of Software Engineering (CMSC 355).\\ Virginia Commonwealth University.}
\newTeaching{2023}{Teaching Assistant}{Introduction to Software Analysis, Testing and Verification (CMSC 525).\\ Virginia Commonwealth University.}
\newTeaching{2020}{Teaching Assistant}{Fundamentals of Software Engineering (CMSC 355).\\ Virginia Commonwealth University.}
\newTeaching{2020}{Teaching Assistant}{Programming Languages (CMSC 403).\\ Virginia Commonwealth University.}
\newTeaching{2015}{Instructor}{Introduction to Mobile Development in Android Studio (8 hours).\\ II SEINFO - Informatics Seminar.}

\section{Awards}
\newAward{2021}{Best Paper Award (Runner Up)}{Journal of Computer Languages (COLA)}
\newAward{2017}{Best Paper Award}{V Workshop on Software Visualization, Evolution and Maintenance (VEM)}

\end{document}
